Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-04-19 manuscript.Rmd
Major updates to plots

@@

```{r imageMaker, comment=NA, echo=FALSE, eval=TRUE}
# Read data files
options(stringsAsFactors = FALSE)
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
hIndex <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/hIndex.csv")

@@

```{r nsf, eval=TRUE}
n.grads <- c(rep(NA, 13), 238, 273, 304, 323, 308, 287, 338, 332,      
    308, 289, 280, NA)
n.grads.1 <- c(rep(NA, 14), 238, 273, 304, 323, 308, 287, 338, 332, 
    308, 289, 280)
n.grads.2 <- c(rep(NA, 15), 238, 273, 304, 323, 308, 287, 338, 332, 
    308, 289)

@@

growth <- c(rep("Unknown", 14), rep("Increase", 2), rep("Decrease", 
    3), "Increase", rep("Decrease", 4), "Unknown")

nsf <- data.frame(cbind(n.grads, n.grads.1, n.grads.2, years))
colnames(nsf) <- c("n.grads", "n.grads.1", "n.grads.2", "years")

```
```{r methodSummaryData, eval=TRUE}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(
        N = n())

@@

articles.otherDocuments <- length(which(full.df$attributes == "article"))
journals.otherDocuments <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))

articles.final <- length(which(full.df$attributes == "article"))
journals.final <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))
```

```{r Table_1, comment=NA, echo=FALSE, eval=TRUE}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(N = n())

@@

```{r finalJournalList}
final.list.updated <- final.list %>% mutate(study.time = 
    as.numeric(last)-as.numeric(first) +1)

final.list.25 <- final.list.updated %>% filter(study.time == 25)

journals.year <- left_join(n.so, n.yr) %>%
    group_by(title)

journals.2012 <- filter(journals.year, year == "2012") %>%
    group_by(title) %>%
    summarize(N = n())

journals.2012 <- arrange(journals.2012, desc(N))
journals.2012$cumS <- cumsum(journals.2012$N)
journals.2012$shortTitle <- factor(c(1:nrow(journals.2012)))

journals.2012$cumperc <- (1:nrow(journals.2012))/nrow(journals.2012) 
journals.2012 <- arrange(journals.2012, desc(N))

journals.2012 <- transform(journals.2012,
                          shortTitle = reorder(shortTitle, 
                                                order(N, decreasing = TRUE)))
ggplot(journals.2012, aes(x = title, y = N)) + 
    geom_bar(stat="identity")

@@

plot.article.count <- ggplot(nsf, aes(as.factor(years), 
    y = n.grads, group=1)) + 
    geom_line(colour="red") + 
    geom_point(colour="red") + 
    #geom_point(colour="red") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Articles") + 
    ggtitle("A. Number of Articles by Year") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    ylim(c(0,2200)) + 
    geom_line(data = articles.year.df, aes(as.factor(years), y = year.count), colour="steelblue") + 
    geom_text(data = nsf, aes(label = n.grads), vjust = 2, size = 2.75) +
    geom_point(data = articles.year.df, aes(as.factor(years), y = articles.year.df$year.count), colour="steelblue") 
```

@@

plot.journal.count <- ggplot(n.journals.year, aes(as.factor(record.y), 
    y = Journal.count, group=1)) + 
    geom_line(colour="black") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    ggtitle("B. Number of Journals by Year") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 70)) +
    annotate("rect", xmin = 2008-1989+1, xmax =  2012-1989+1, 
    ymin = 55, ymax = 70, alpha = .20, fill= "#0072B2") +
    annotate("rect", xmin = 2005-1989+1, xmax =  2007-1989+1, 
    ymin = 53, ymax = 62, alpha = .20, fill = "#0072B2")  
```

```{r plothIndex, eval=TRUE}
final.list.index <- within(final.list.index, quartile <- as.integer(cut(h5Index, quantile(h5Index, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))

@@

plotIndex <- ggplot(final.list.index, aes(x = n, y = h5Index )) + 
    geom_point(aes(colour=factor(quartile), size = years), alpha=.80) +
    geom_smooth()

@@

n_authors2$ID <- as.factor(c(1989:2013))

n_authors2_melted <- reshape2::melt(n_authors2, id.vars = "ID")
colnames(n_authors2_melted) <- c("pubYear", "summaryStat", "value")

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

plot.author.count <- ggplot(n_authors2_melted, aes(x = pubYear, y = value, group = summaryStat, colour = summaryStat)) + 
    geom_line(size = .75) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10), 
    legend.title=element_blank()) +
    scale_colour_manual(values=cbPalette)  +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(limits = c(0,2.5)) +
    ylab("Value") +
    xlab("Year") +
    ggtitle("Authors Per Article by Year")
```

```{r}

authorNames  <- filter(full.df, attributes == "author")

@@

```{r pages, eval=TRUE}
pages.tmp <- full.df %>% filter(attributes == "pages")
years.tmp <- full.df %>% filter(attributes == "pubYear")
pages.df <- left_join(pages.tmp, years.tmp, by = "articleID") %>% 
    select(record.y, record.x) %>%
    rename(years = record.y, pages = record.x) %>%
    mutate(pages = as.numeric(pages)) %>%
    group_by(years) %>%
    summarise(
        Median.Pages = median(pages, na.rm=TRUE), 
        Mean.Pages = mean(pages, na.rm=TRUE),
        Std.Pages = sd(pages, na.rm=TRUE))

pages.df.melted <- reshape2::melt(pages.df, id.vars = "years")

@@

```{r pages.plot, eval=TRUE}

page.plot <- ggplot(pages.df.melted, aes(years, value, group = 
    variable, color=variable)) + 
    geom_line() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10), 
    legend.title=element_blank()) +
    scale_colour_manual(values=cbPalette)  +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(limits = c(0,16)) +
    ylab("Value") +
    xlab("Year") +
    ggtitle("Article Length by Year")
```

```{r nsfPlot, eval=TRUE}
plot.PhD <- ggplot(nsf, aes(years, n.grads, group=1)) + 
    geom_line(linetype="dotted", colour = "#0072B2", size = .75) + 
    geom_point(colour = "#0072B2", size = .75) +
    scale_y_continuous(breaks = c(seq(0, 350, 25)), limits = c(200,350)) +
    ylab("Doctoral degrees") +
    xlab("Year") +
    geom_text(aes(label = n.grads), vjust = -1.2, size = 2.75) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10)) +
    ggtitle("Number of Earned Social Work Doctoral Degrees by Year") 
```

>>>>

```{r colorThemes}
# http://colorbrewer2.org/?type=diverging&scheme=PuOr&n=4

cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
```

@@

```{r cleaningFunctions, comment=NA, echo=FALSE, eval=TRUE}
# Read data files
options(stringsAsFactors = FALSE)
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
hIndex <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/hIndex.csv")
hIndex$h5Index <- ifelse(is.na(hIndex$h5Index), 0, hIndex$h5Index)
hIndex$h5Median <- ifelse(is.na(hIndex$h5Median), 0, hIndex$h5Median)

@@

```{r dataNSF, eval=TRUE}
n.grads <- c(rep(NA, 13), 238, 273, 304, 323, 308, 287, 338, 332,      
    308, 289, 280, NA)

@@

nsf <- data.frame(cbind(n.grads,  years))
colnames(nsf) <- c("n.grads", "years")
```

```{r tableArticleSummary, eval=TRUE}
unique.titles <- filter(full.df, attributes == "journal") %>%
    group_by(record) %>%
    summarise(N = n())

@@

articles.otherDocuments <- length(which(full.df$attributes == "article"))

journals.otherDocuments <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))

articles.final <- length(which(full.df$attributes == "article"))

journals.final <- filter(full.df, attributes == "journal") %>% 
    summarise(Unique = n_distinct(record))

@@

final.list.index$h5Index <- ifelse(is.na(final.list.index$h5Index), 0,final.list.index$h5Index)
x <- ggplot(final.list.index, aes(x =reorder(title, n), y = n, colour = h5Index)) + geom_point(stat="identity") + coord_flip() + 
    theme_bw()

@@

#Annotation data file
articles.x <- as.factor(articles.year.df[c(1, 6, 12, 18, 25), 1]) 
articles.y <- articles.year.df[c(1, 6, 12, 18, 25), 2] 
articles.label <- as.character(articles.y)
articles.placement <- articles.y-50

plot.article.count <- ggplot(nsf, aes(as.factor(years), 
    y = n.grads, group=1)) + 
    geom_line(colour="red") + 
    geom_point(colour="red") + 
    #geom_point(colour="red") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Articles") + 
    ggtitle("A. Number of Articles by Year") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    ylim(c(0,2200)) + 
    geom_line(data = articles.year.df, aes(as.factor(years), y = year.count), colour="steelblue") + 
    #geom_text(data = nsf, aes(label = n.grads), vjust = 2, size = 2.75) +
    geom_point(data = articles.year.df, aes(as.factor(years), y = articles.year.df$year.count), colour="steelblue") + 
    annotate("text", factor(c(2002, 2005, 2008, 2012)), 
    c(165, 225, 250, 190) + 150, label = c("238","323", "338", "280") , size = 3) + 
    annotate("text", articles.x, articles.placement, label = articles.label, size=3)

@@

plot.journal.count <- ggplot(n.journals.year, aes(as.factor(record.y), 
    y = Journal.count, group=1)) + 
    geom_line(colour="black") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    ggtitle("B. Number of Journals by Year") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 70)) 
```

```{r plotH-Index, eval=TRUE}
final.list.index <- within(final.list.index, quartile <- as.integer(cut(h5Index, quantile(h5Index, probs=0:4/4, na.rm=TRUE), include.lowest=TRUE)))

@@

plotIndex <- ggplot(final.list.index, aes(x = n, y = h5Index )) + 
    geom_point(aes(colour=factor(quartile), size = years), alpha=.80) +
    geom_smooth() + 
    scale_colour_manual(values=cp)

@@

n_authors2$year <- as.factor(c(1989:2013))

cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )

plot.author.count <- ggplot(n_authors2, aes(x = year, group=1)) + 
    geom_line(aes(y=Median, colour="Median"), size = .75, colour = "#fdb864", alpha = .70) + 
    geom_line(aes(y=Average, colour = "Average"), size = .75,  colour = "#e66101" ) +
    geom_point(aes(y=Average, size = Standard_Deviation), colour = "#e66101") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10)) +  
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(limits = c(0,2.5)) +
    ylab("Value") +
    xlab("Year") +
    ggtitle("Authors Per Article by Year") +
    labs(size = "Standard deviation") 
```

```{r authorNames}
authorNames  <- filter(full.df, attributes == "author")

@@

```{r pagePlot, eval=TRUE}
pages.tmp <- full.df %>% filter(attributes == "pages")
years.tmp <- full.df %>% filter(attributes == "pubYear")
pages.df <- left_join(pages.tmp, years.tmp, by = "articleID") %>% 
    select(record.y, record.x) %>%
    rename(years = record.y, pages = record.x) %>%
    mutate(pages = as.numeric(pages)) %>%
    group_by(years) %>%
    summarise(
        Median.Pages = median(pages, na.rm=TRUE), 
        Mean.Pages = mean(pages, na.rm=TRUE),
        Std.Pages = sd(pages, na.rm=TRUE))
cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )

page.plot <- ggplot(pages.df, aes(years, Mean.Pages, size = Std.Pages, group = 1))+ 
    geom_line(size=.75, colour =  "#5e3c99") +
    geom_line(aes(years, Median.Pages, group = 1), size = .75, colour = "#b2abd2", alpha = .70) + 
    geom_point(colour = "#5e3c99") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10)) +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(limits = c(11,16)) +
    ylab("Value") +
    xlab("Year") +
    labs(size = "Standard deviation", colour = "Median")  +
    ggtitle("Article Length by Year")

@@
